Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-02 src/article.tex
Spell check

Synteny methods compare the assembled contigs to a more complete reference
genome sequence searching for areas of sequence similarity between the two.
Areas of corresponding sequence between the two sets can be used to infer
contig placement and build the contigs into a scaffold
\cite{richter2007,zhao2008,assefa2009}. Recombination between the two genomes
can, however, reduce the effectiveness of this analysis. Repeat regions may
also be responsible for many of the gaps in building a genome sequence. The
existence of tandemly repeated nucleotide regions produces many similar reads
fromgenome sequencing. The assembly of reads generated from repeat regions can
result in the assembly collapsing into a single repeat instance or ignored by
more conservative assembly algorithms. These regions may however be resolved by
using reassembly algorithms specifically for repeat resolution
\cite{mulyukov2002,koren2010}. Similarly a related approach may use unassembled
sequence reads matching the regions around a scaffold gap to construct
a uniquely overlapping set of reads across the gap \cite{tsai2010}. \pb

@@

The software outlined here, ``Scaffolder'', aims to address these problems by
creating a file syntax and software framework for editing a genome scaffold.
Scaffolder uses a specific file format to define how contigs are joined,
additional sequences inserted, and for the specification of unknown regions.
This syntax allows a scaffold to be updated by simply editing the scaffold
file. Scaffolder facilites a reproducible scaffolding process and provides
a concise overview of how the scaffold was constructed. \pb

>>>>

Synteny methods compare the assembled contigs to a more complete reference
genome sequence searching for areas of sequence similarity between the two.
Areas of corresponding sequence between the two sets can be used to infer
contig placement and build the contigs into a scaffold
\cite{richter2007,zhao2008,assefa2009}. Recombination between the two genomes
can, however, reduce the effectiveness of this analysis. Repeat regions may
also be responsible for many of the gaps in building a genome sequence. The
existence of tandemly repeated nucleotide regions produces many similar reads
from genome sequencing. The assembly of reads generated from repeat regions can
result in the assembly collapsing into a single repeat instance or ignored by
more conservative assembly algorithms. These regions may however be resolved by
using reassembly algorithms specifically for repeat resolution
\cite{mulyukov2002,koren2010}. Similarly a related approach may use unassembled
sequence reads matching the regions around a scaffold gap to construct
a uniquely overlapping set of reads across the gap \cite{tsai2010}. \pb

@@

The software outlined here, ``Scaffolder'', aims to address these problems by
creating a file syntax and software framework for editing a genome scaffold.
Scaffolder uses a specific file format to define how contigs are joined,
additional sequences inserted, and for the specification of unknown regions.
This syntax allows a scaffold to be updated by simply editing the scaffold
file. Scaffolder facilitates a reproducible scaffolding process and provides
a concise overview of how the scaffold was constructed. \pb
